Project Code

### 2020-05-12 project.Rmd
more analysis

```{r libraries, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F)
library(stringi) # %s+%
library(lubridate) # floor_date
library(xts) # zoo
library(fpp) # auto.arima
library(tidyverse) # map_df, read_csv, group_by, summarize
library(tsbox) # https://cran.r-project.org/web/packages/tsbox/vignettes/tsbox.html
print_dec <- function(x, decimals=2) trimws(format(round(x, decimals), nsmall=decimals))

@@

```{r import dataset, include=FALSE}
# UCCS
domain <- c(-350000,350000); pattern <- "UCCS.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"
# MEMS
# domain <- c(-7200,7200); pattern <- "MEM.*.csv"; name <- "MEM"; description <- "Membach"
seis <-
  list.files(path="csv/", pattern=pattern) %>%
  map_df(~read_csv("csv/" %s+% .))
```

@@

@@

```{r}
seis.h.start <- as_datetime('2018-10-29T00:00:00')
seis.h.end <- as_datetime('2020-03-01T00:00:00')
seasonality.period <- 168
seis.h.ts <- build_ts(seis.h, periods = c(seasonality.period), start = seis.h.start, end = seis.h.end, force_ms = T)
autoplot(seis.h.ts, main = "Hourly seismic movement", xlab = "Weeks", ylab = "mean movement (nm)")
hist(seis.h.ts)
autoplot(acf(seis.h.ts, na.action=na.pass, plot=F))
autoplot(pacf(seis.h.ts, na.action=na.pass, plot=F))

```
Once notice the composition is additive (the fluctuations does not seem to grow with the trend)
```{r}
dec.addi <- decompose(na.aggregate(seis.h.ts, floor))
autoplot(dec.addi)
dec.multi <- decompose(log(na.aggregate(seis.h.ts, floor)))
autoplot(dec.multi)
autoplot(acf(dec.addi$random, na.action=na.omit, plot=F))
autoplot(acf(dec.multi$random, na.action=na.omit, plot=F))
autoplot(pacf(dec.addi$random, na.action=na.omit, plot=F))
autoplot(pacf(dec.multi$random, na.action=na.omit, plot=F))
```

@@

```{r}
p <- floor(seasonality.period/2)
weights <- rep(1/(2*p+1), times=2*p+1)
trend <- stats::filter(seis.h.ts, sides=2, filter = weights)
```

```{r show_overlap_and_diff, include=FALSE}
show_overlap_and_diff <- function(base, compare, base.desc, compare.desc, xlab, overlap.ylab, diff.title, diff.ylab, diff.ylab.sec, diff.ylab.sec.accuracy=.1) {
  overlap_plot <-
    autoplot(compare, xlab=xlab, ylab=overlap.ylab) +
      geom_line(aes(y=base, col="red"), show.legend = F)
  span <- max(compare, base, na.rm = T) - min(compare, base, na.rm = T)
  diff <- compare-base
  diff_plot <-
    autoplot(diff, ylab = paste0("Difference (", diff.ylab, ")"), xlab = xlab) +
      labs(title = diff.title, subtitle = paste0(base.desc, " - ", compare.desc)) +
      scale_y_continuous(sec.axis = sec_axis(~./span, name=paste0("Difference (", diff.ylab.sec, ")"), labels = scales::percent_format(accuracy = diff.ylab.sec.accuracy))) +
      geom_hline(yintercept=mean(diff, na.rm=T), linetype="dashed", color = "red")
  return(list(overlap_plot, diff_plot))
}
```

And they match:
```{r}
plots <- show_overlap_and_diff(
  dec.addi$trend, trend, xlab="Weeks",
  base.desc = "additive decomposition",
  compare.desc = paste0("linear filtered trend with p=", p),
  overlap.ylab = "Trend (nm)",
  diff.title = "Difference between trends",
  diff.ylab = "nm", diff.ylab.sec="% over trend span"
)
plots[[1]]
plots[[2]]

@@

```{r}
f <- seasonality.period
weights.s <- c(0.5, rep(1,f-1), 0.5)/f
trend.s <- stats::filter(seis.h.ts, side=2, filter=weights.s)

plots <- show_overlap_and_diff(
  dec.addi$trend, trend.s, xlab="Weeks",
  base.desc = "additive decomposition",
  compare.desc = paste0("shift-filtered trend with f=", f),
  overlap.ylab = "Trend (nm)",
  diff.title = "Difference between trends",
  diff.ylab = "nm", diff.ylab.sec="% over trend span",
  diff.ylab.sec.accuracy = .001
)
plots[[1]]
plots[[2]]

@@

```{r}
detrended <- na.aggregate(seis.h.ts, floor)-trend.s
detrended <- window(detrended, end = c(end(detrended)[1], seasonality.period), extend=T)
matrix <- t(matrix(data = detrended, nrow = seasonality.period))
seasonality.figure <- as.ts(colMeans(matrix, na.rm = T))
seasonality <- rep(seasonality.figure, length(detrended)/length(seasonality.figure))[1:length(trend.s)]
```

@@

plots <- show_overlap_and_diff(
  dec.addi$figure, seasonality.figure, xlab="Hours",
  base.desc = "additive decomposition",
  compare.desc = paste0("mean-over-period after removal of shift-filtered trend with f=", f),
  overlap.ylab = "Seasonality (nm)",
  diff.title = paste0("Difference between seasonalities (f=", seasonality.period, ")"),
  diff.ylab = "nm", diff.ylab.sec="% over seasonality span"
)
plots[[1]]
plots[[2]]

@@

```{r}
residuals <- seis.h.ts - trend.s - seasonality

plots <- show_overlap_and_diff(
  dec.addi$random, residuals, xlab="Weeks",
  base.desc = "additive decomposition",
  compare.desc = paste0("mean-over-period after removal of shift-filtered trend with f=", f),
  overlap.ylab = "Residuals (nm)",
  diff.title = paste0("Difference between residuals (f=", seasonality.period, ")"),
  diff.ylab = "nm", diff.ylab.sec="% over residuals span"
)
plots[[1]]
plots[[2]]

@@

```{r}
ts <- residuals+trend+seasonality

plots <- show_overlap_and_diff(
  seis.h.ts, ts, xlab="Weeks",
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span"
)
plots[[1]]
plots[[2]]

@@

```{r}
acf(residuals, na.action = na.omit)
pacf(residuals, na.action = na.omit)
seis.h.ts.ar <- Arima(seis.h.ts, c(1,0,0))
tsdiag(seis.h.ts.ar)
```

```{r}
seis.h.start <- with_tz(as_datetime('2018-11-01T00:00:00'), "Europe/Brussels")
seis.h.end <- with_tz(as_datetime('2020-03-01T00:00:00'), "Europe/Brussels")
seis.h.msts <- na.aggregate(build_ts(seis.h, periods = c(24, 168), start = seis.h.start, end = seis.h.end, force_ms = T))
seis.h.msts %>% mstl() %>% autoplot() + xlab("Week")
seis.h.msts.mstl <- seis.h.msts %>% mstl()
plot(seis.h.msts.mstl[,2], main="trend")
lines(trend.s, col="red")
plot(rowSums(seis.h.msts.mstl[,3:4]), main="seasonality",type="l")
lines(c(rep(seasonality,seasons), seasonality[1:(((length(detrended)/168-seasons)*168))]), col="red")
plot(residuals,  main="residuals")
lines(seis.h.msts.mstl[,5], col="red")
autoplot(seis.h.msts.mstl[,5])
acf(seis.h.msts.mstl[,5], na.action = na.omit)
bptests <- c()
for (i in 1:10)
  bptests<- c(bptests, Box.test(seis.h.msts.mstl[,5], lag = i, fitdf = 0, type = "Box-Pierce")$p.value)
plot(bptests, ylim = c(0,1))
abline(h=0.05,col="blue",lty="dotted")

@@

>>>>

```{r libraries, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.height = 360)
library(stringi) # %s+%
library(lubridate) # floor_date
library(xts) # zoo
library(fpp) # auto.arima
# library(gridExtra) # for gg-plotting multiple plots
library(cowplot) # for plot_grid
library(tidyverse) # map_df, read_csv, group_by, summarize
library(tsbox) # https://cran.r-project.org/web/packages/tsbox/vignettes/tsbox.html
print_dec <- function(x, decimals=2) trimws(format(round(x, decimals), nsmall=decimals))

@@

```{r import dataset, include=FALSE}
# MEMS
domain <- c(-7200,7200); pattern <- "MEM.*.csv"; name <- "MEM"; description <- "Membach"
# UCCS
domain <- c(-350000,350000); pattern <- "UCCS.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"
seis <-
  list.files(path="csv/", pattern=pattern) %>%
  map_df(~read_csv("csv/" %s+% .))
```

@@

Box.test(forec$model$residuals, type="Box-Pierce")

@@

```{r plot data with (p)acf}
seis.h.start <- as_datetime('2018-10-29T00:00:00')
seis.h.end <- as_datetime('2020-03-01T00:00:00')
seasonality.period <- 24
seasonality.xlab <- "Days"
seasonality.aggregate <- function(ds) na.aggregate(seis.h.ts, function(x) floor(x/7))
seasonality.period <- 168
seasonality.xlab <- "Weeks"
seasonality.aggregate <- function(ds) na.aggregate(ds, floor)
seis.h.ts <- build_ts(seis.h, periods = c(seasonality.period), start = seis.h.start, end = seis.h.end, force_ms = T)
plot_grid(
  autoplot(seis.h.ts, main = "Hourly seismic movement", xlab = seasonality.xlab, ylab = "mean movement (nm)"),
  gghistogram(seis.h.ts) + xlab("mean movement (nm)"),
  nrow = 2)
plot_grid(
  autoplot(acf(seis.h.ts, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  autoplot(pacf(seis.h.ts, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  nrow = 2)

```
Once notice the composition is additive (the fluctuations does not seem to grow with the trend)
```{r decompose}
dec.addi <- decompose(seasonality.aggregate(seis.h.ts))
autoplot(dec.addi) + labs(title="Decomposition of additive time series", subtitle = paste0("Seasonality ", seasonality.period))
dec.multi <- decompose(log(seasonality.aggregate(seis.h.ts)))
autoplot(dec.multi) + labs(title="Decomposition of multiplicative time series (log-scale additive)", subtitle = paste0("Seasonality ", seasonality.period))
plot_grid(
  autoplot(acf(dec.addi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  autoplot(acf(dec.multi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  nrow = 2)
plot_grid(
  autoplot(pacf(dec.addi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  autoplot(pacf(dec.multi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  nrow = 2)
```

@@

```{r linear trend}
p <- floor(seasonality.period/2)
weights <- rep(1/(2*p+1), times=2*p+1)
trend <- stats::filter(seasonality.aggregate(seis.h.ts), sides=2, filter = weights)
```

```{r show_overlap_and_diff, include=FALSE}
show_overlap_and_diff <- function(base, compare, base.desc, compare.desc, xlab, overlap.ylab, diff.title, diff.ylab, diff.ylab.sec, diff.ylab.sec.accuracy=.1) {
  overlap_plot <-
    autoplot(compare, xlab=xlab, ylab=overlap.ylab) +
      geom_line(aes(y=base, col="red"), show.legend = F) +
      labs(title=paste0(base.desc, " vs ", compare.desc))
  span <- max(compare, base, na.rm = T) - min(compare, base, na.rm = T)
  diff <- compare-base
  accu.lims <- diff.ylab.sec.accuracy / 100 * span * c(-3,3)

  mse <- mean(diff^2)
  mae <- mean(abs(diff))
  rmse <- sqrt(mse)
  R2 <- 1-(sum((diff)^2)/sum((base-mean(base))^2))
  errorstring <- paste0("MSE=", mse, "    MAE=", mae, "    RMSE=", rmse, "    R2=", R2)
  print(errorstring)

  diff_plot <-
    autoplot(diff, ylab = paste0("Difference (", diff.ylab, ")"), xlab = xlab) +
      expand_limits(y=accu.lims) +
      labs(title = diff.title, subtitle = paste0(base.desc, " - ", compare.desc)) +
      scale_y_continuous(sec.axis = sec_axis(~./span, name=paste0("Difference (", diff.ylab.sec, ")"), labels = scales::percent_format(accuracy = diff.ylab.sec.accuracy))) +
      geom_hline(yintercept=mean(diff, na.rm=T), linetype="dashed", color = "red")
  return(list(overlap_plot, diff_plot))
}
```

And they match:
```{r linear trend plot}
plots <- show_overlap_and_diff(
  dec.addi$trend, trend, xlab=seasonality.xlab,
  base.desc = "additive decomposition trend",
  compare.desc = paste0("linear filtered trend with p=", p),
  overlap.ylab = "Trend (nm)",
  diff.title = "Difference between trends",
  diff.ylab = "nm", diff.ylab.sec="% over trend span"
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

```{r trend MA}
f <- seasonality.period
weights.s <- c(0.5, rep(1,f-1), 0.5)/f
trend.s <- stats::filter(seasonality.aggregate(seis.h.ts), side=2, filter=weights.s)

plots <- show_overlap_and_diff(
  dec.addi$trend, trend.s, xlab=seasonality.xlab,
  base.desc = "additive decomposition trend",
  compare.desc = paste0("shift-filtered trend with f=", f),
  overlap.ylab = "Trend (nm)",
  diff.title = "Difference between trends",
  diff.ylab = "nm", diff.ylab.sec="% over trend span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

```{r trend figure}
detrended <- seasonality.aggregate(seis.h.ts)-trend.s
detrended <- window(detrended, end = c(end(detrended)[1], seasonality.period), extend=T)
matrix <- t(matrix(data = detrended, nrow = seasonality.period))
seasonality.figure <- as.ts(colMeans(matrix, na.rm = T))
seasonality <- rep(seasonality.figure, length(detrended)/length(seasonality.figure))[1:length(trend.s)]
```

@@

```{r difference of trend figure}

plots <- show_overlap_and_diff(
  dec.addi$figure, seasonality.figure, xlab=seasonality.xlab,
  base.desc = "additive decomposition",
  compare.desc = paste0("mean-over-period after removal of shift-filtered trend with f=", f),
  overlap.ylab = "Seasonality (nm)",
  diff.title = paste0("Difference between seasonalities (f=", seasonality.period, ")"),
  diff.ylab = "nm", diff.ylab.sec="% over seasonality span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

```{r residuals}
residuals <- seasonality.aggregate(seis.h.ts) - trend.s - seasonality

plots <- show_overlap_and_diff(
  dec.addi$random, residuals, xlab=seasonality.xlab,
  base.desc = "additive decomposition",
  compare.desc = paste0("mean-over-period after removal of shift-filtered trend with f=", f),
  overlap.ylab = "Residuals (nm)",
  diff.title = paste0("Difference between residuals (f=", seasonality.period, ")"),
  diff.ylab = "nm", diff.ylab.sec="% over residuals span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

residuals.acf <- autoplot(acf(residuals, na.action = na.pass, plot=F)) + scale_x_continuous()
residuals.pacf <- autoplot(pacf(residuals, na.action = na.pass, plot=F)) + scale_x_continuous()
plot_grid(residuals.acf, residuals.pacf, nrow=2)

@@

```{r difference of reconstruct}
ts <- residuals+trend.s+seasonality

plots <- show_overlap_and_diff(
  seis.h.ts, ts, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

plots <- show_overlap_and_diff(
  seis.h.ts, dec.addi$trend+dec.addi$seasonal+dec.addi$random, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

```{r extract both 24 and 168}
trend.s_compute <- function(ts.in, period) {
  f <- period
  weights.s <- c(0.5, rep(1,f-1), 0.5)/f
  trend.s <- stats::filter(ts.in, side=2, filter=weights.s)
  return(trend.s)
}

season_by_mean <- function(ts.in, period) {
  freq <- frequency(ts.in)
  if (freq == period) {
    end <- c(end(ts.in)[1], period)
  } else {
    end <- c(((end(ts.in)[1] * freq) %/% period + 1) * (period/freq), freq)
  }
  extended <- window(ts.in, end = end, extend=T)
  matrix <- t(matrix(data = extended, nrow = period))
  seasonality.figure <- as.ts(colMeans(matrix, na.rm = T))
  seasonality <- rep(seasonality.figure, length(extended)/length(seasonality.figure))[1:length(ts)]
  return(list(figure=seasonality.figure, seasonal=seasonality))
}

trend_season <- function(ts.in, period) {
  trend.s <- trend.s_compute(ts.in, period)
  season <- season_by_mean(ts.in-trend.s, period)
  season$trend <- trend.s
  return(season)
}

aggregated <- seasonality.aggregate(seis.h.ts)
season.24 <- trend_season(aggregated, 24)
season.168 <- trend_season(aggregated-season.24$seasonal, 168)

plot_grid(
  autoplot(aggregated) + ylab("") + xlab(""),
  autoplot(ts(season.24$seasonal, frequency=24)) + ylab("") + xlab(""),
  autoplot(ts(season.168$seasonal, frequency=24)) + ylab("") + xlab(""),
  autoplot(ts(season.168$trend, frequency=24)) + ylab("") + xlab(""),
  autoplot(aggregated-season.24$seasonal-season.168$seasonal-season.168$trend) + ylab("") + xlab(""),
  nrow = 5)

season.24 <- trend_season(aggregated-season.168$seasonal, 24)
season.168 <- trend_season(aggregated-season.24$seasonal, 168)

season.24 <- trend_season(aggregated-season.168$seasonal, 24)
season.168 <- trend_season(aggregated-season.24$seasonal, 168)

plot_grid(
  autoplot(aggregated) + ylab("") + xlab(""),
  autoplot(ts(season.24$seasonal, frequency=24)) + ylab("") + xlab(""),
  autoplot(ts(season.168$seasonal, frequency=24)) + ylab("") + xlab(""),
  autoplot(ts(season.168$trend, frequency=24)) + ylab("") + xlab(""),
  autoplot(aggregated-season.24$seasonal-season.168$seasonal-season.168$trend) + ylab("") + xlab(""),
  nrow = 5)

seasonbase.24 <- trend_season(aggregated, 24)
seasonbase.168 <- trend_season(aggregated, 168)

plot_grid(
  autoplot(ts(seasonbase.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
      geom_line(aes(y=season.24$figure, col="red"), show.legend = F),
  autoplot(ts(seasonbase.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
      geom_line(aes(y=season.168$figure, col="red")) +
      geom_line(aes(y=season.168$figure + rep(season.24$figure, 7), col="blue")),
  nrow = 2)

plots <- show_overlap_and_diff(
  seasonbase.168$figure, season.168$figure + rep(season.24$figure, 7), xlab="Hours",
  base.desc = "168 from ds",
  compare.desc = "168+24 from ds",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between 168",
  diff.ylab = "nm", diff.ylab.sec="% over season span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

```{r test_ts}
seis.test.start <- as_datetime('2019-05-20T00:00:00')
seis.test.end <- as_datetime('2020-03-02T00:00:00')

seis.h.test <- build_ts(seis.h, periods = c(seasonality.period), start = seis.test.start, end = seis.test.end, force_ms = T)
```

```{r diffs acf/pacf}
seis.h.test %>% ggtsdisplay(lag.max = 168)
seis.h.test %>% diff() %>% ggtsdisplay(lag.max = 168*5)
# seis.h.test %>% diff(D=2) %>% ggtsdisplay(lag.max = 168)
# seis.h.test %>% diff(lag=24) %>% ggtsdisplay(lag.max = 168)
# seis.h.test %>% diff() %>% diff(lag=24) %>% ggtsdisplay(lag.max = 24, main="Supposed model: ARIMA(24,1,0)(0,1,2)[24]") # ARIMA(0,1,0)(0,1,2)[24]
# previous => ARIMA(5,1,0)(0,1,7)[24]
# seis.h.test %>% diff() %>% diff(lag=24, D=2) %>% ggtsdisplay(lag.max = 168)
seis.h.test %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*5) # arima (0,0,0)(0,1,1/2)[168]
seis.h.test %>% diff() %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*5) # arima (0,1,0)(0,1,1)[168]
# seis.h.test %>% diff() %>% diff(lag=168, D=2) %>% ggtsdisplay(lag.max = 168)
seis.h.test %>% diff() %>% diff(lag=24) %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168)
```

```{r arima}

plot_forecast <- function(forec) {
  BP <- Box.test(forec$model$residuals, type="Box-Pierce")
  autoplot(forec) +
    labs(title=forec$method, subtitle = paste0("Box-Pierce p-value=", print_dec(BP$p.value, decimals=4))) +
    autolayer(forec$mean, series="Forecast") -> plotted
  return(plotted)
}

to_test <- list(
  #c(0,0,0,0,0,1),  # BAD, Box-Pierce = 0
  #c(0,0,0,0,0,2),  # BAD, Box-Pierce = 0
  #c(0,0,0,0,1,1),  # nice, Box-Pierce = 0
  c(0,0,0,0,1,2),
  #c(0,0,0,0,1,3),  # CAN'T BE DONE: 3*168 = 504 > 350 (limit of arima on r)
  #c(0,1,0,0,0,1),  # BAD, Box-Pierce = 0
  c(0,1,0,0,1,1),
  c(0,1,0,0,1,2),
  c(2,0,0,0,1,0),  # hint from auto.arima D=1
  c(5,0,0,0,1,0),  # hint from auto.arima D=1
  c(3,1,1,0,1,0),  # hint from auto.arima D=1 d=1
  c(3,1,1,0,1,1),  # after hint then ACF + PACF
)
if (!exists("models")){
  models <- list()
}
for (model in to_test) {
  model <- c(3,1,1,0,1,1)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  print("SARIMA(" %s+% paste0(model[1:3], collapse = ",") %s+% ")(" %s+% paste0(model[4:6], collapse = ",") %s+% ")[" %s+% frequency(seis.h.test) %s+% "]")
  models[[fit.name]] <- Arima(seis.h.test, model[1:3], model[4:6])
  models[[forecast.name]] <- forecast(models[[fit.name]], h=168*10)
}
models[["fitauto"]] <- auto.arima(seis.h.test, D=1, approx=F, trace = T)
models[["forecastauto"]] <- forecast(models[["fitauto"]], h=168*10)
models[["fit311010"]] <- models[["fitauto"]]
models[["forecast311010"]] <- forecast(models[["fit311010"]], h=168*10)

# 000012 better than 000011, Box-Pierce = 0
plotting.model <- models[["fit000012"]]
plotting.forecast <- models[["forecast000012"]]
# 010011 somehow better somehow worst than 000012, Box-Pierce = 0
plotting.model <- models[["fit010011"]]
plotting.forecast <- models[["forecast010011"]]
# 010012 , Box-Pierce = 
plotting.model <- models[["fit010012"]]
plotting.forecast <- models[["forecast010012"]]
# 311010 , Box-Pierce = 
plotting.model <- models[["fit311010"]]
plotting.forecast <- models[["forecast311010"]]
# 311011 , Box-Pierce = 
plotting.model <- models[["fit311011"]]
plotting.forecast <- models[["forecast311011"]]

checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)
plot_forecast(plotting.forecast)
plots <- show_overlap_and_diff(
  seis.h.test, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

plotting.model <- models[["fit010012"]]
plotting.forecast <- models[["forecast010012"]]
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)
plot_forecast(plotting.forecast)
plots <- show_overlap_and_diff(
  seis.h.test, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

```{r}
(seis.test.start - seis.first.second)

deseasoned24 <- seis.h.ts - seasonality
autoplot(deseasoned24)
frequency(deseasoned24)
de24.test <- msts(window(deseasoned24, start=205), seasonal.periods = c(168))
frequency(de24.test)
autoplot(de24.test)
de24.test %>% ggtsdisplay(lag.max = 168*2)
de24.test %>% diff() %>% ggtsdisplay(lag.max = 168*2)
de24.test %>% diff(D=2) %>% ggtsdisplay(lag.max = 168*2)
de24.test %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*2)
de24.test %>% diff() %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*2, main="Supposed model: ARIMA(0,1,0)(0,1,1)[168]")
de24.test %>% diff() %>% diff(lag=168, D=2) %>% ggtsdisplay(lag.max = 168*2)

if (!exists("fit010011de")){
  fit010011de <- Arima(de24.test, c(0,1,0), c(0,1,1))
}
checkresiduals(fit010011de)
residuals.acf <- autoplot(acf(fit010011de$residuals, na.action = na.pass, plot=F, lag.max=168*3)) + scale_x_continuous()
residuals.pacf <- autoplot(pacf(fit010011de$residuals, na.action = na.pass, plot=F, lag.max=168*3)) + scale_x_continuous()
plot_grid(residuals.acf, residuals.pacf, nrow=2)
if (!exists("fit010011de.forec")){
  fit010011de.forec <- forecast(fit010011de, h=168*10)
}
plot_forecast(forecast(fit010011de.forec, h=168*10))

# NO  fit011011de <- Arima(de24.test, c(0,1,1), c(0,1,1))
if (!exists("fit011011de")){
  fit011011de <- Arima(de24.test, c(0,1,1), c(0,1,1))
  arima
}
fit010011de$aic
fit011011de$aic
checkresiduals(fit011011de)
residuals.acf <- autoplot(acf(fit011011de$residuals, na.action = na.pass, plot=F, lag.max=168*3)) + scale_x_continuous()
residuals.pacf <- autoplot(pacf(fit011011de$residuals, na.action = na.pass, plot=F, lag.max=168*3)) + scale_x_continuous()
plot_grid(residuals.acf, residuals.pacf, nrow=2)
if (!exists("fit011011de.forec")){
  fit011011de.forec <- forecast(fit011011de, h=168*10)
}
plot_forecast(forecast(fit011011de.forec, h=168*10))

seis.test.start <- as_datetime('2019-05-20T00:00:00')
seis.test.end <- as_datetime('2020-03-02T00:00:00')

seis.h.test <- build_ts(seis.h, periods = c(seasonality.period), start = seis.test.start, end = seis.test.end, force_ms = T)

# First seasonal difference (quarterly)
# seasonality.arima <- 24
D<-1
seis.h.test.ds<-diff(seis.h.test,differences=D)
plot(seis.h.test.ds)
abline(h=mean(seis.h.test.ds), col="red", lty="dotted")
sd(seis.h.test.ds)
tsdisplay(seis.h.test.ds, lag.max = 168*2)
autoplot(acf(seis.h.test.ds, plot=F, lag.max = 168*2)) + scale_x_continuous()
autoplot(pacf(seis.h.test.ds, plot=F, lag.max = 168*2)) + scale_x_continuous()
seis.h.test.ds<-diff(seis.h.test,lag=seasonality.period,differences=D)
plot(seis.h.test.ds)
abline(h=mean(seis.h.test.ds), col="red", lty="dotted")
sd(seis.h.test.ds)
autoplot(acf(seis.h.test.ds, plot=F, lag.max = 168*2)) + scale_x_continuous()
autoplot(pacf(seis.h.test.ds, plot=F, lag.max = 168*2)) + scale_x_continuous()
tsdisplay(seis.h.test.ds, lag.max = 168*2)
# pacf cuts off after p=168
```

```{r}
fit <- auto.arima(seis.h.test, d=1, D=1, trace = T, parallel = T)
```
 Fitting models using approximations to speed things up...

 ARIMA(2,0,2)(1,1,1)[24] with drift         : Inf
 ARIMA(0,0,0)(0,1,0)[24] with drift         : 111462.7
 ARIMA(1,0,0)(1,1,0)[24] with drift         : 101954.4
 ARIMA(0,0,1)(0,1,1)[24] with drift         : Inf
 ARIMA(0,0,0)(0,1,0)[24]                    : 111460.9
 ARIMA(1,0,0)(0,1,0)[24] with drift         : 102426.5
 ARIMA(1,0,0)(2,1,0)[24] with drift         : 101379
 ARIMA(1,0,0)(2,1,1)[24] with drift         : Inf
 ARIMA(1,0,0)(1,1,1)[24] with drift         : Inf
 ARIMA(0,0,0)(2,1,0)[24] with drift         : 110647.6
 ARIMA(2,0,0)(2,1,0)[24] with drift         : 101332.9
 ARIMA(2,0,0)(1,1,0)[24] with drift         : 101878.7
 ARIMA(2,0,0)(2,1,1)[24] with drift         : Inf
 ARIMA(2,0,0)(1,1,1)[24] with drift         : Inf
 ARIMA(3,0,0)(2,1,0)[24] with drift         : 101317.9
 ARIMA(3,0,0)(1,1,0)[24] with drift         : 101858.5
 ARIMA(3,0,0)(2,1,1)[24] with drift         : Inf
 ARIMA(3,0,0)(1,1,1)[24] with drift         : Inf
 ARIMA(4,0,0)(2,1,0)[24] with drift         : 101302.7
 ARIMA(4,0,0)(1,1,0)[24] with drift         : 101845
 ARIMA(4,0,0)(2,1,1)[24] with drift         : Inf
 ARIMA(4,0,0)(1,1,1)[24] with drift         : Inf
 ARIMA(5,0,0)(2,1,0)[24] with drift         : 101305.4
 ARIMA(4,0,1)(2,1,0)[24] with drift         : 101304.5
 ARIMA(3,0,1)(2,1,0)[24] with drift         : 101307.7
 ARIMA(5,0,1)(2,1,0)[24] with drift         : 101307.7
 ARIMA(4,0,0)(2,1,0)[24]                    : 101300.7
 ARIMA(4,0,0)(1,1,0)[24]                    : 101843
 ARIMA(4,0,0)(2,1,1)[24]                    : Inf
 ARIMA(4,0,0)(1,1,1)[24]                    : Inf
 ARIMA(3,0,0)(2,1,0)[24]                    : 101316
 ARIMA(5,0,0)(2,1,0)[24]                    : 101303.4
 ARIMA(4,0,1)(2,1,0)[24]                    : 101302.4
 ARIMA(3,0,1)(2,1,0)[24]                    : 101305.8
 ARIMA(5,0,1)(2,1,0)[24]                    : 101305.7

 Now re-fitting the best model(s) without approximations...

 ARIMA(4,0,0)(2,1,0)[24]                    : 101586.6

 Best model: ARIMA(4,0,0)(2,1,0)[24]

```{r}
library(car)

autoplot(acf(seis.h.test.ds, plot=F, lag.max = 168*2)) + scale_x_continuous()
autoplot(pacf(seis.h.test.ds, plot=F, lag.max = 168*2)) + scale_x_continuous()

qqPlot(fit$residuals)
gghistogram(fit$residuals)
Box.test(fit$residuals, type="Box-Pierce")
fit.forec <- forecast(fit, h=24*10)
plot(fit.forec, xlim=c(250, 300))

frequency(seis.h.test)
p<-168;d<-0;q<-0;P<-0;D<-1;Q<-0;
paste0("ARIMA(", p, ",", d, ",", q, ")(", P, ",", D, ",", Q, ")_", frequency(seis.h.test))
fit <- Arima(seis.h.test, order=c(p,d,q), seasonal=c(P,D,Q))
fit
#Diagnostics
tsdisplay(residuals(fit), lag.max=168*2)

p<-1;d<-0;q<-2;P<-1;D<-0;Q<-2;
fit <- Arima(seis.h.test, order=c(p,d,q), seasonal=c(P,D,Q))
#Diagnostics
tsdisplay(residuals(fit))
forecast()
